### 2021-02-17 evaluation.tex
experimenty, prvni stranka, poznamky a mirne reformulace

To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
a series of experiments was performed.
%\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ... Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ... }
In this section, we describe the design and configuration of the experiments,
and then compare the performance of the trained models to baseline heuristics.

@@

The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
Vampire was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
Vampire was modified to allow the user to specify the predicate and function symbol precedences
for the proof search.
\todo[inline]{FB: Add a link to the modified Vampire.}

@@

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
\todo{FB: Justify saturation loop iterations as a proxy for success.}
\todo{FB: Reference a detailed explanation of saturation loop iterations.}

Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo},
\todo{FB: Consider omitting LPO completely if we don't discuss it anywhere in the paper.}
ever compares a predicate symbol with a function symbol,
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
A predicate precedence recommender is trained separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
\todo{FB: Weak, handwavy spot. Consider improving the argumentation.}
This section describes how the training data for training a \emph{predicate} precedence recommender is generated.
Training data for training a function precedence recommender is generated analogously.

>>>>

% !TEX root = main.tex

To demonstrate the capacity of the precedence recommender described in \cref{sec:architecture},
a series of experiments was performed.
%\todo{MS: vzdycky kdyz to jen trochu jde, snaz se pouzivat cinny rod (a pritomny cas): To demonstrate ..., we performed ... Ale taky tu trochu chybi, co nas ceka dal, ve stylu: In this section, we report ... }
In this section, we describe the design and configuration of the experiments,
and then compare the performance of the trained models to baseline heuristics.
\todo{MS: az na to ``was performed'' dobry! ;)}

@@

The empirical evaluation was performed using a modified version of the \gls{atp} Vampire 4.3.0 \cite{10.1007/978-3-642-39799-8_1}.
The prover was used to generate the training data and to evaluate the trained precedence recommender.
To generate the training data,
Vampire was modified to output \gls{cnf} representations of the problems
and annotated problem signatures in a machine-readable format.
%in \gls{json} format and annotated problem signatures in \gls{csv} format.\todo{MS: Mentioning JSON or CSV seems to be too low level. ``programmer documatation'' material.}
For the evaluation of the precedences generated by the recommender,
Vampire was modified to allow the user to supply explicit predicate and function symbol precedences for the proof search
(normally, the user only picks a precedence generation heuristic).
\todo[inline]{FB: Add a link to the modified Vampire.}

@@

The training data consists of examples of the form $(P, \PrecBetter, \PrecWorse)$,
where $P$ is a \gls{cnf} problem and $\PrecBetter, \PrecWorse$ are precedences of symbols of problem $P$
such that out of the two precedences, $\PrecBetter$ yields a proof in fewer iterations of the saturation loop.
\todo{FB: Justify saturation loop iterations as a proxy for success. MS: Ano, ale driv nez zde!}
\todo{FB: Reference a detailed explanation of saturation loop iterations. MS: podobne jako v PAAR clanku. Dal bych to nekam okolo prelim.}

Since neither of the common \glspl{sot}, i.e., \gls{kbo} nor \gls{lpo},
\todo{FB: Consider omitting LPO completely if we don't discuss it anywhere in the paper.}
ever compares a predicate symbol with a function symbol,
two separate precedences can be considered for each problem:
a predicate precedence and a function precedence.
We trained a predicate precedence recommender separately from a function precedence recommender
to simplify the training process and to isolate the effects of the predicate and function precedences.
\todo{FB: Weak, handwavy spot. Consider improving the argumentation. MS: tady activum dokonce pomuze 
stim weak spotem. "A recommender is trained separately, because" zni trochu jako "autorita predepisuje delate to prave takto,
protoze <dobre duvody>". Kdyz reknes "we trained, because", ty duvodu uz mohou byt pouze prakticke a ctenar to pochopi! }
This section describes how the training data for training a \emph{predicate} precedence recommender was generated.
Training data for training a function precedence recommender was generated analogously.
\todo{MS: taky jsem to hodil do minuleho casu. Myslim, ze to je opet blizsi skutecnosti: V Cestine:
"Takhle jsme to delali" (at vite, co presne kritizovat) vs "Takhle se to dela" (kritika pak muze byt o dost silnejsi,
protoze jakoby tvrdis, ze prezentujes spravnou metodiku).}
